### 2013-09-27 main.tex
set binding correction to 2cm (as this is the total correction).
more minor fixes

\documentclass[12pt,toc=bibnumbered, a4paper,twoside,DIV=11,BCOR=1cm]{scrbook}
%\documentclass[12pt,toc=bibnumbered, a4paper,twoside,DIV=calc]{scrbook}
%\documentclass[12pt,toc=bibnumbered, a4paper,twoside]{book}

@@

principle is simple: the process of prediction \emph{using a given inference

@@

and decision tree fields~\citep{nowozin2011decision}, based on decision trees.

@@

interesting. Decision tree fields~(DTFs) on the other hand have been applied to loopy

@@

inputs and labelings, introducing higher order potentials or latent variables
allow the model to express more complex interactions within the output
variables~\citep{dann2012pottics, kohli2009robust}. Possible examples are
consistency of larger regions, learning parts or learning of scene classes and
cooccurences.

@@

attention, while approaches using latent variables are often limited by
the non-convexity of learning.  It would be interesting to compare current
methods using latent variable and higher order approaches, and see how these
interact with different inference and learning schemes.

>>>>

\documentclass[12pt,toc=bibnumbered, a4paper,twoside,DIV=11,BCOR=2cm]{scrbook}
%\documentclass[12pt,toc=bibnumbered, a4paper,twoside,DIV=calc]{scrbook}
%\documentclass[12pt,toc=bibnumbered, a4paper,twoside]{book}

@@

principle is simple: the process of \emph{prediction using a given inference

@@

and decision tree fields~(DTFs)~\citep{nowozin2011decision}, based on decision trees.

@@

interesting. DTFs on the other hand have been applied to loopy

@@

inputs and labelings, introducing higher order
potentials~\citep{kohli2009robust, ladicky2009associative} or latent
variables~\citep{dann2012pottics} allow the model to express more complex
interactions within the output variables. Possible examples are consistency of
larger regions, learning parts or learning of scene classes and cooccurences.

@@

attention, while approaches using latent variables are often limited by the
non-convexity of learning.  It would be interesting to compare current methods
using latent variable and higher order approaches, and see how these interact
with different inference and learning schemes.
